### 2013-09-26 manuscripts/reply/reply.tex
Making correction in reply.
Changing `\locusMutationRateScalar` to `\locusRateHetShapeParameter` in
the list of uniformly-distributed priors.
commit attempt 3

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that their methodology suffered from a fundamental error that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate how their approach still suffers from a bias
    toward models with lesser parameter space, which manifests in a dangerously
    strong tendency to sample predominantly from models that exclude the true
    values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

@@

\newpage
\noindent Recently, this journal has served as a medium for an interesting
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses that
revealed that \msb can often be biased towards inferring models of temporally
clustered divergence times among taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb.
They conclude the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian perspective
towards model choice and questionable assumptions, and does not explain the
bias of the method found in many of the analyses of \citet{Oaks2012}.
Furthermore, we reiterate several of the findings of \citet{Oaks2012} as well
as present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of the method.

As for how to mitigate the bias, \citet{Oaks2012} suggest that more cogent
prior probability distributions on divergence models and nuisance parameters
could reduce the effect of Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially if any
biological conclusions are drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the method is biased and dangerous.  The approach
merely provides another means by which the model can ``escape'' large parameter
space, and bias toward smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is used and encouraged by
\citet{Hickerson2013} without any mention of its potential complications.

\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

@@

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}).
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an approximate
Bayesian model choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how being limited to uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  \citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

This is not to say that empirical Bayesian approaches are not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more questionable.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.

\subsection*{Practical dangers of narrow uniform priors for Bayesian model
choice}
We were alarmed when we saw the results of the model-averaging approach
used by \citet{Hickerson2013}.
Their results strongly favored the models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This concerned us because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa.
They set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it seems odd to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, when we saw the results of \citet{Hickerson2013} we suspected that
Lindley's paradox was again biasing the method toward models with smaller
parameter space, and as a consequence was biasing the method toward models that
exclude the truth (i.e., toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model).

We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn form an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with lesser parameter space,
but rather allows it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}).
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).

@@

\subsection*{Final thoughts on empirical priors in Bayesian model choice}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigator's choice of priors after having seen the resulting posterior.
In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analysing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two the these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012}.
\highLight{Any new stuff to add to this list of citations?}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before
performing the analysis.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that \cwlnote{their}{the} methodology \cwlnote{suffered}{of \citet{Hickerson2013}} suffers from a fundamental error that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate how \cwlnote{their}{the} approach \cwlnote{}{of \citet{Hickerson2013}} still suffers from a bias
    toward models with \cwlnote{lesser}{less} parameter space, which manifests in a dangerously
    strong tendency to sample predominantly from models that exclude the true
    values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

@@

\newpage

\highLight{The goal of this paper needs to be to highlight the major differences of opinion on how ABC can be used in comparative phylogeography and how these changes to msbayes can be made that will improve the inference in the future. We should avoid nit-picking the Hickerson paper and try to stay positive.}

\noindent Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses that
revealed that \msb can often be biased towards inferring models of temporally
clustered divergence times among taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement with \citet{Hickerson2013} reiterating a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest it is intrinsic to \msb, concluding the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that the empirical Bayesian approach used by \citet{Hickerson2013} is based on questionable assumptions, and does not explain the
bias of the method found in many of the analyses of \citet{Oaks2012}. 
Furthermore, we show that the model-averaging approach suggested by \citet{Hickerson2013} does not correct the bias towards small priors and we present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of \msb.

%This paragraph seems too aggressive. It also seems to repeat some of the previous points. I removed it for now.

%To mitigate the bias, \citet{Oaks2012} suggest that more cogent
%prior probability distributions on divergence models and nuisance parameters
%could reduce the effect of Lindley's paradox.
%They also layout a set of simulation-based procedures for determining power,
%accuracy, and robustness of the method given a dataset, and recommend any
%application of \msb should be accompanied by such procedures, especially if any
%biological conclusions are drawn from the results.
%\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
%for accommodating uncertainty in selecting among empirically guided priors, and
%champion the method as a means of avoiding the pitfalls raised by
%\citet{Oaks2012}.
%Unfortunately, we show that fundamental errors in this approach render some of
%their results invalid and leave the remaining results difficult to interpret.
%Furthermore, we follow the advice of \citet{Oaks2012} and present
%simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
%approach.
%Our results demonstrate that the new method of \citet{Hickerson2013} is biased and dangerous.  The approach
%merely provides another means by which the model can ``escape'' large parameter
%space, and bias toward smaller models remains.
%This manifestation of the bias can be dangerous and often excludes the true
%parameter space due to the use of narrow uniform priors.
%Furthermore we discuss the potential theoretical and practical problems of
%empirical Bayesian model choice, which is used and encouraged by
%\citet{Hickerson2013} without any mention of its potential complications.

%It may be important to point out the error made in their paper, but it can also be nit-picky, it depends on how the error impacts the overall message of our response. 
%We should strive to keep the response short and directed at the big picture items. If there is a way to still point out the error, then maybe some of this section should be used
\iffalse
\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

@@

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}).

\cwlnote{}{This part seems important, but not related to the error in units discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an approximate
Bayesian model choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.
\fi

@@

\iffalse
\section*{The dangers of empirical Bayesian model choice}

\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''. 
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail that the limitation in using uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, \textit{a priori}.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.
\fi

\section*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}

Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief \cwlnote{}{is belief the right term in this section? Would probability or likelihood be better?}
 that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to many powerful inference methods.
Unfortunately, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is unclear.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

%I like the example, but it may be too cute. It is also too long. I think a contrived example is good, but if there could be an example that is more relevant to model choice and comparison of inaccurate posterior distributions, I think that would be better. This is an example of empirical Bayes, but not the potential problem with the use in msbayes. Unless I am interpreting wrong. I would be careful about making it to cute as well. You may intend to make it easy to understand for a general audience, but it can also seem like talking down to Hickerson et al, who we are responding to. It just depends on how you read it.
\iffalse
This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while they tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirically informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.
\fi

\subsection*{Dangers of narrow uniform priors for Bayesian model
choice} \cwlnote{}{Should this be part of the empirical Bayes section, or something else?}

\cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes approaches for model choice when using uniform priors can exclude the $truth$ from the prior, which is a violation of Bayes theorem" or something like that. Picking apart what they calculated and we calculated seems like too much detail. I would try to simplify how this is being presented. This can lead into how the use of more appropriate prior distributions should be used.}
The results of \citet{Hickerson2013} reanalysis of the Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
The narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate
Lindley's paradox is biasing the method toward models with smaller
parameter space, and as a consequence is biasing the method toward models that
exclude the truth (i.e., toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model).

%This should be in the section on model-averaging, not empirical Bayes limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with less parameter space,
but rather allows it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}).
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).

@@

\subsection*{Final thoughts on empirical priors in Bayesian model choice}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigator's choice of priors after having seen the resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before
performing the analysis.

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
\cwlnote{}{I think the empirical use of the model-averaging should go here, instead of above in the empirical Bayes section}
